Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-07-16 drafts/outline.tex
working on methods

%\chapter{Introduction}
%
%TODO
%
%
%\chapter{Results}
%
%TODO
%
%\chapter{Discussion}
%
%TODO
%
%The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$ in comparison to greased dowels. The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$). However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.

\setcounter{chapter}{3}

@@

We chose to use granular walnut shell flour to simulate sediment for our experiments because of the availability of homogeneous, sieve-measured grain sizes in suitable quantities. We performed preliminary experiments with a range of grain sizes but settled on WF5-200 as an appropriate match for sediment sizes in natural floodplains. We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA). Median particle size was determined to be \SI{25.2}{\micro\metre} (Figure \ref{fig:sedsize}).

\begin{figure}[htbp]
\includegraphics[width=15cm,trim = {0 3cm 0 0},clip]{wf5-200sizedist.png}
\centering
\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right). The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.}
\label{fig:sedsize}
\end{figure}

>>>>

%\chapter{Introduction}
%
%TODO
%
%\chapter{Results}
%
%TODO
%
%\chapter{Discussion}
%
%TODO
%
%The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$ in comparison to greased dowels. The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$). However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.

\setcounter{chapter}{1}

@@

We chose to use granular walnut shell flour to simulate sediment for our experiments because of the availability of homogeneous, sieve-measured grain sizes in suitable quantities. We performed preliminary experiments with a range of grain sizes but settled on WF5-200 as an appropriate match for sediment sizes in natural floodplains. We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA). Median particle size was determined to be approximately \SI{25}{\micro\metre} (Figure \ref{fig:sedsize}).

\begin{figure}[htbp]
\includegraphics[width=15cm,trim = {0 3cm 0 0},clip]{wf5-200sizedist.png}
\centering
\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right). The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.} %TODO get rid of red X's and make a clean, high-res version of figure
\label{fig:sedsize}
\end{figure}
